%-------------------------
% Resume in Latex
% Author : Priyanshu K Sharma
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}%\setmainfont{Times New Roman}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage[T1]{fontenc}
% \usepackage[T1]{fontenc}
% \usepackage{cochineal}
% \usepackage{fourier}

% \usepackage{fontspec}
% \usepackage{polyglossia}
% \setmainlanguage{german}
% \setmainfont{Times New Roman}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSingleSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------\usepackage{fontspec}
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------


\begin{center}
    {\huge Priyanshu Kumar Sharma} \\ \vspace{2pt} 
    {+91 93923 81422} ~ 
    \small{-}
    \href{priyanshu17ks@gmail.com}{\color{blue}{priyanshu17ks@gmail.com}} ~ 
    \small{-}
    \href{https://www.linkedin.com/in/priyanshu-kumar-sharma-333800251/}{ \color{blue}{LinkedIn}}  ~
    \small{-}
    \href{https://github.com/PriyanshuKSharma/}{ \color{blue}{GitHub}} ~
    \small{-}
    \href{https://hub.docker.com/u/priyanshuksharma}{\color{blue}{DockerHub}} ~
    \vspace{-7pt}
\end{center}

%-----------EDUCATION-----------
\section{\color{airforceblue}EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ajeenkya D Y Patil University}{Pune, India}
      {B.Tech in (IT) Cloud Technology and Information Security {| CGPA:9.89}}{Aug 2022 - Ongoing}
    \vspace{-4pt}
     \resumeSubheading
      {Sri Chaitanya Jr. Kalasala}{Hyderabad, India}
      {Higher Secondary Education {| Percentage: 93.9}}{April 2020 - May 2022}
    \vspace{-4pt}
     \resumeSubheading
      {Sri Chaitanya High School}{Hyderabad, India}
      {Secondary Education {| Percentage: 87.6}}{April 2018 - March 2020}

    
  \resumeSubHeadingListEnd
  \vspace{-10pt}

%-----------PROGRAMMING SKILLS-----------
\section{\color{airforceblue}TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{\normalsize{Programming Languages:}}{ \normalsize{C, Python, Java, Dart, SQL, Shell Scripting}} \\
      \vspace{1.8pt}

      \textbf{\normalsize{Development:}}{ \normalsize{HTML, CSS, Flutter}} \\
      \vspace{1.8pt}

      \textbf{\normalsize{DevOps Tools:}}{ \normalsize{Git/GitHub, Terraform, Pulumi, GitLab, Redis}} \\
      \vspace{1.8pt}

      \textbf{\normalsize{Cybersecurity Tools:}}{ \normalsize{Nmap, Nslookup, Lynis, Wireshark, SQLmap, Metasploit}} \\
      \vspace{1.8pt}

      \textbf{\normalsize{Cloud Computing:}}{ \normalsize{AWS, Azure}} \\
      \vspace{1.8pt}
      
     \textbf{\normalsize{Languages:}}{ \normalsize{English, Hindi, Gujarati}}

     % copy and paste above textbf block to add more 
     }}
 \end{itemize}
 \vspace{-16pt}
 
 %-----------EXPERIENCE-----------
\section{\color{airforceblue}WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Network Security Associate Virtual Intern}{} 
      {\textbf{EduSkills Foundation, Pune}}{July 2024 - September 2024}
      \resumeItemListStart
            \resumeItem{\normalsize{Completed the \textbf{Fortinet Network Security Associate Virtual Internshi}p, organized by \textbf{AICTE and EduSkills.}}}
            \resumeItem{\normalsize{Gained knowledge in network security principles and their application in protecting network infrastructures.}}  
            \resumeItem{\normalsize{Developed skills in identifying and mitigating network threats and vulnerabilities.}}
            \resumeItem{\normalsize{Learned about the latest trends and best practices in network security.}}
            
      \resumeItemListEnd  
      \vspace{2pt}
      
    \resumeSubheading
      {Cloud Research Intern}{} 
      {\textbf{Indian Institute of Technology Ropar, Punjab} }{May 2024 - July 2024}
      \resumeItemListStart
            \resumeItem{\normalsize{Involved in research projects under an IIT professor}}
            \resumeItem{\normalsize{Working on the implementation of \textbf{XFBench} and \textbf{XFaaS.}}}  
            \resumeItem{\normalsize{Developing serverless function implementation.}}
            \resumeItem{\normalsize{Conducting performance analysis and optimisation of serverless functions.}}
            \resumeItem{\normalsize{Part of the \textbf{Summer Research Fellowship Program}, 2024 by the \textbf{Indian Academy of Science, Bangalore}.}}
      \resumeItemListEnd
      \vspace{2pt}
      
    \resumeSubheading
      {Cloud Security Virtual Intern}{} 
      {\textbf{EduSkills Foundation, Pune }}{April 2024 - June 2024}
      \resumeItemListStart
            \resumeItem{\normalsize{Completed the \textbf{Zscaler Zero Trust Cloud Security Virtual Internship}, organised by \textbf{AICTE} and \textbf{EduSkills}.}}
            \resumeItem{\normalsize{Gained knowledge in \textbf{Zero Trust Principles} and their application in cloud security.}}  
            \resumeItem{\normalsize{Developed skills in securing cloud environments and protecting data assets.}}
            \resumeItem{\normalsize{Learned about the latest trends and best practices in cloud security.}}
      \resumeItemListEnd  

    % copy and paste above resumeSubheading block to add more 
  \resumeSubHeadingListEnd
\vspace{-12pt}


 %-----------PROJECTS-----------
\section{\color{airforceblue}PROJECTS}    
    \resumeItemListStart
        \vspace{0.5pt}
        
        \resumeItem{\normalsize{\textbf{Quantum Cloud Integration}, Developed a hybrid cloud-quantum system integrating cloud computing with quantum processing for enhanced computational efficiency. 
        \newline 
        Features:
        \begin{itemize}
            \item Workflow integration between classical cloud and quantum systems.
            \item Secure and scalable hybrid cloud implementation.
            \item \textbf{Tools Used:} AWS, IBM Quantum, and Docker.
        \end{itemize}} 
        \href{https://github.com/PriyanshuKSharma/quantum-cloud-integration}{\color{blue}\underline{GitHub}}}
        \vspace{2.5pt}

        \newpage
        \resumeItem{\normalsize{\textbf{AI-Powered SaaS Platform}, Built a \textbf{Software-as-a-Service (SaaS) platform} leveraging AI to provide automated business solutions. 
        \newline
        Features:
        \begin{itemize}
            \item Integrated \textbf{Machine Learning models} to analyze user data and provide actionable insights.
            \item Full-stack development using \textbf{React.js, Node.js, and Python}.
        \end{itemize}
        Tech Stack:
        \begin{itemize}
            \item \textbf{Framework:} Next.js 14
            \item \textbf{Styling:} Tailwind CSS
            \item \textbf{Database:} Prisma, Neon DB (PostgreSQL)
            \item \textbf{Authentication:} Clerk
            \item \textbf{Video Storage:} Cloudinary
            \item \textbf{Deployment:} Vercel
        \end{itemize}} 
        \href{https://github.com/PriyanshuKSharma/ai-powered-saas.git}{\color{blue}\underline{GitHub}}}
        \vspace{2pt}

        
        \resumeItem{\normalsize{\textbf{SkyVault}, Built a personal cloud storage system using Docker containers, providing an interactive UI. 
        \newline
        Features:
        \begin{itemize}
            \item File uploading, listing, and downloading functionalities.
            \item Dockerized deployment for easy scalability.
            \item Secure authentication and data storage.
            \item \textbf{Tools Used:} Flask, HTML, CSS and Docker.
        \end{itemize}} 
        \href{https://github.com/PriyanshuKSharma/SkyVault}{\color{blue}\underline{GitHub}}}
        \vspace{2pt}
        
        \resumeItem{\normalsize{\textbf{Ecobizz: An E-commerce App}, An app built using Dart language and Flutter SDK. 
        \newline
        Features:
        \begin{itemize}
            \item Runs on both iOS and Android devices.
            \item A platform for sustainable products.
        \end{itemize}}  
        \href{https://github.com/PriyanshuKSharma/EcoBizz-Sustainably-Yours---GDSC-Solution-Challenge-2024.git}{\color{blue}\underline{GitHub}}}
        \vspace{2pt}
        
        \resumeItem{\normalsize{\textbf{Li-Fi Tech}, Research work about Light Fidelity. 
        \newline
        Features:
        \begin{itemize}
            \item A new way to share information.
            \item Developed an IoT device through which messages can be passed using light instead of Wi-Fi.
        \end{itemize}} 
        \href{https://github.com/PrajwalUlli/LiFi.git}{\color{blue}\underline{GitHub}}}
        
        
        
    \resumeItemListEnd \vspace{2pt}
%


%-----------EXTRACURRICULAR---------------
\section{\color{airforceblue}EXTRA-CURRICULAR ACTIVITIES}
    
      \resumeItemListStart
        \resumeItem{\normalsize{\textbf{Vice President} in Matheletes(Maths Club) - {March 2023 - July 2025} }} 
        \vspace{-5pt}
        
        \resumeItem{\normalsize{\textbf{Core Member} in Happier and Safer Internet Club - } {October 2023 - October 2024}}    
        \vspace{-5pt}

        % copy and paste above resumeItem block to add more 
      \resumeItemListEnd 


%-----------CERTIFICATIONS---------------
\section{\color{airforceblue}CERTIFICATIONS}
    
      \resumeItemListStart
        \resumeItem{\normalsize{\href{https://training.fortinet.com/pluginfile.php/1/tool_certificate/issues/1725205245/0255279459PS.pdf}{\textbf{Fortinet Certified Fundamentals in Cybersecurity}}}}
        \vspace{-5pt}
        \resumeItem{\normalsize{\href{https://training.fortinet.com/pluginfile.php/1/tool_certificate/issues/1726054380/8105663001PS.pdf}{\textbf{Fortinet Certified Associate in Cybersecurity}}}}
        \vspace{-5pt}
        \resumeItem{\normalsize{\href{https://verify.skilljar.com/c/ki8nr3rcqek6}{\textbf{Zscaler: Fundamentals of Cybersecurity (EDU-102)}}}}
        \vspace{-5pt}
        \resumeItem{\normalsize{\href{https://verify.skilljar.com/c/s439vf56ibca}{\textbf{Zscaler: Zero Trust Certified Associate (ZTCA)}}}}
        \vspace{-5pt}
        

        % copy and paste above resumeItem block to add more 
      \resumeItemListEnd

  % copy and paste above resumeItem block to add more 
\resumeItemListEnd 





\vspace{-12pt}

\end{document}
